The title

### 2023-04-04 doc/manuscript_data_imp_log.Rmd
Abstract tables and figures

```{r load-targets, include=FALSE}
tar_load(model_list_by_age_data_imp)
tar_load(data_clean)
tar_load(purdy_pictures_by_age_data_imp)
tar_load(model_tables_age_data_imp)
tar_load(demog_table)
pretty <- function(x) format(x, big.mark = ",")

@@

```{r sleep-outcomes}
papaja::apa_table(
  model_tables_age_data_imp$sleep$data,
  caption = model_tables_age_data_imp$sleep$caption,
  note = model_tables_age_data_imp$sleep$note,
  col_spanners = model_tables_age_data_imp$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on physical activity volume. The panels on the left show the curvilinear relationship between PA volume and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero. These plots demonstrate exact turning points where the effects of PA volume change by age."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_pa_volume), error = FALSE)
```

@@

```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on physical activity intensity. The panels on the left show the curvilinear relationship between PA intensity and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_pa_intensity), error = FALSE)
```

@@

```{r pa-outcomes}
papaja::apa_table(
  model_tables_age_data_imp$physical_activity$data,
  caption = model_tables_age_data_imp$physical_activity$caption,
  note = model_tables_age_data_imp$physical_activity$note,
  col_spanners = model_tables_age_data_imp$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration. The panels on the left show the curvilinear relationship between sleep duration and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_sleep_duration_lag), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency. The panels on the left show the curvilinear relationship between sleep efficiency and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_sleep_efficiency_lag), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset. The panels on the left show the curvilinear relationship between sleep onset and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_sleep_onset_lag), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity. The panels on the left show the curvilinear relationship between sleep regularity and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp)$predictor_sleep_regularity_lag), error = FALSE)
```

>>>>

```{r load-targets, include=FALSE}
tar_load(model_list_by_age_data_imp_log)
tar_load(data_clean)
tar_load(purdy_pictures_by_age_data_imp_log)
tar_load(model_tables_age_data_imp_log)
tar_load(demog_table)
pretty <- function(x) format(x, big.mark = ",")

@@

```{r sleep-outcomes}
papaja::apa_table(
  model_tables_age_data_imp_log$sleep$data,
  caption = model_tables_age_data_imp_log$sleep$caption,
  note = model_tables_age_data_imp_log$sleep$note,
  col_spanners = model_tables_age_data_imp_log$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on physical activity volume. The panels on the left show the curvilinear relationship between PA volume and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero. These plots demonstrate exact turning points where the effects of PA volume change by age."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_pa_volume), error = FALSE)
```

@@

```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on physical activity intensity. The panels on the left show the curvilinear relationship between PA intensity and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_pa_intensity), error = FALSE)
```

@@

```{r pa-outcomes}
papaja::apa_table(
  model_tables_age_data_imp_log$physical_activity$data,
  caption = model_tables_age_data_imp_log$physical_activity$caption,
  note = model_tables_age_data_imp_log$physical_activity$note,
  col_spanners = model_tables_age_data_imp_log$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration. The panels on the left show the curvilinear relationship between sleep duration and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_sleep_duration_lag), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency. The panels on the left show the curvilinear relationship between sleep efficiency and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_sleep_efficiency_lag), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset. The panels on the left show the curvilinear relationship between sleep onset and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_sleep_onset_lag), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity. The panels on the left show the curvilinear relationship between sleep regularity and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(tar_read(purdy_pictures_by_age_data_imp_log)$predictor_sleep_regularity_lag), error = FALSE)
```
